---
title: "cim_w_v_manuscript"
output: html_document
---

---
title             : "Variation of [v] in Cook Islands Māori"
shorttitle        : "Cook Islands Māori"

author: 
  - name          : "Quartz Colvin"
    affiliation   : "Rutgers University"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "quartz.colvin@rutgers.edu"

affiliation:
  - id            : "1"
    institution   : "Rutgers University"

author_note: >
  Complete departmental affiliations for each author (note the indentation, if you start a new paragraph).

  Enter author note here.

abstract: >
  ???.
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes

lang              : "english"
class             : "man"
output            : papaja::apa6_word
---

```{r include = FALSE}
#| label: setup-libs

library("tidyverse")
library("tidyr")
library("here")
library("papaja")

source(here::here("scripts", "libs.R"))

untidy_data <- read_csv(here("untidy_data", "cim-v-w-202410.csv"))

```


```{r, 'source-libs', echo=FALSE}
source("../scripts/libs.R")
```


# Introduction

???write-intro

**Hypotheses to test**

**1. Is w associated with more voicing (f0 at different points) than v?**

**2. Is w associated with higher intensity than v?**

**3. Is w associated with a longer duration than v?**














\clearpage

# Methods

Participants???

Material???

Procedure???

# Data

???fill-in

```{r}
#| label: glimpse-cim

head(untidy_data)

```

???tidy-data

```{r}
#| label: tidy-cim
#| message: false
#| warning: false

dat <- untidy_data |>
  drop_na() |>   # remove rows that have NA values
  filter(TextGridLabel == "v") |>
  arrange(island, Word) |>   # group by island
  select(island, word = Word, f0_20 = f0_20.point, f0_50 = f0_50.point, f0_80 = f0_80.point, duration, intensity = intensity_midpoint) |>
  write_csv("tidy_cim.csv")

```

**Here is the tidy data, but not the whole table because it is quite lengthy???**

```{r}
#| label: show-tidy-data
#| warning: false
#| message: false

knitr::kable(head(dat))

```


# Analysis

???fill-in

## duration by island 

???fill-in

```{r}
#| label: duration-by-island
#| warning: false
#| message: false

mod1 <- lm(formula = duration ~ island, data = dat) |>
  ggplot() +
  aes(x = island, y = duration, color = island) +
  geom_boxplot()

print(mod1)

```

```{r}
#| label: avg-dur
#| message: false
#| warning: false

mean(dat$duration)

```


## intensity by island

???fill-in

```{r}
#| label: intensity-by-island
#| warning: false
#| message: false

mod2 <- lm(formula = intensity ~ island, data = dat) |>
  ggplot() +
  aes(x = island, y = intensity, color = island) +
  geom_boxplot()

print(mod2)

```


```{r}
#| label: avg-intensity
#| message: false
#| warning: false

mean(dat$intensity)

```

### summary

???fill-in

```{r}
#| label: descriptive-stats
#| warning: false
#| message: false

summary(mod1)

summary(mod2)

```


## f0 trajectories by island 

**do the same thing the paper i did my online pres on. plot all the f0 values on y axis and time on x axis, color by island**

```{r}
#| label: f0_dur_mod
#| warning: false
#| message: false

mod_f0 <- dat |>
  ggplot() + 
  aes(x = duration, y = f0_20, color = island) +
  geom_point(alpha = 0.2) +
  geom_smooth(
    method = "glm", 
    family = poisson(link = "log"))

print(mod_f0)

```


### Data analysis


We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
